Reading episode files and preparing data sets

### 2025-05-13 data-raw/01-preprocessing-episode-files.Rmd
Fixing 2022 data set columns format

for (col in names(walking_2015)) {
  target_class <- class(walking_2015[[col]])
  walking_2022[[col]] <- match.fun(paste0("as.", target_class[1]))(walking_2022[[col]])
}
```

@@

for (col in names(walking_2015)) {
  target_class <- class(walking_2015[[col]])
  cycling_2022[[col]] <- match.fun(paste0("as.", target_class[1]))(cycling_2022[[col]])
}
```

>>>>

numeric_columns <- c("WGHT_EPI")

int_columns <- c("PUMFID", "ACTCODE", "STARTIME", "ENDTIME", "DURATION",
                     "origin", "destination", "LUC_RST",  "PRV")

for (col in numeric_columns) {
  walking_2022[[col]] <- as.numeric(as.character(walking_2022[[col]]))
}

for (col in int_columns) {
  walking_2022[[col]] <- as.integer(as.character(walking_2022[[col]]))
}
```

@@

for (col in numeric_columns) {
  cycling_2022[[col]] <- as.numeric(as.character(cycling_2022[[col]]))
}

for (col in int_columns) {
  cycling_2022[[col]] <- as.integer(as.character(cycling_2022[[col]]))
}
```
